Coalition Formation Algorithm of Prosumers in a Smart Grid Environment

### 2014-09-15 Article.tex
update Nico

In this model, we consider that only the coalitions that have this probability value sufficiently low are acceptable. That this, we denote by $ \phi \in [0,1] $ the threshold imposed to the coalitions over this quantity, and we call it the \textbf{reliability} in the following. The reliability stipulates then that for any coalition S willing to join the market, the probability of S value (at any instant t) being below its contract value should at most be $ \phi $. That is, $ \forall S,\ \forall t,\ Pr[P_{S}(t) \leq P_{S}^{CRCT} ] \leq \phi $ ($ \phi $ being restricted to small values for consistency).

>>>>

In this model, we consider that only the coalitions that have this probability value sufficiently low are acceptable. That is, we denote by $ \phi \in [0,1] $ the threshold imposed to the coalitions over this quantity, and we call it the \textbf{reliability} in the following. The reliability stipulates then that for any coalition S willing to join the market, the probability of S value (at any instant t) being below its contract value should at most be $ \phi $. That is, $ \forall S,\ \forall t,\ Pr[P_{S}(t) \leq P_{S}^{CRCT} ] \leq \phi $ ($ \phi $ being restricted to small values for consistency).
